More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-10-18 2016-Weak-FH-Bisim/WeakBisim.tex
Proof of corollary V1

By construction, four substitutions $\subst{~}$ only have an effect on the  
variables of the open automaton they belong to, they also produce terms containing only 
variables of the open automaton they belong to. Finally, because of the domain of the 
substitutions  and of the predicates, we have:\\
       	$\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	\Leftrightarrow % we changed =
       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
       	\Pred_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	\Leftrightarrow % we changed = 
       	 \Pred\!'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $\\

@@

\TODO{Lemma revu mais convaincant...}

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, \WTUn\ allows us to obtain a similar redution with $n_1=1$): 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT \bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots n_1].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where \\
$ 
s=s^1_0 \wedge s^1_{n_1}\!=s_1,
\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n_1} \vis{\set{\beta^1_i}}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1\\
$

@@

such that\\
$
s_i^6= \left\{
 \begin{array}{ll}
s_i^1 & \mbox{if }i<n_1\\
s_{i-n_1}^3 & \mbox{if }i\geq n_1\\
\end{array}
\right. \, \wedge \,
s_i^8= \left\{
 \begin{array}{ll}
s_i^2 & \mbox{if }i<m_1\\
s_{i-m_1}^5 & \mbox{if }i\geq m_1\\
\end{array}
\right. \\
s\!=\!s^6_0 \wedge s^6_{n_1+n_2}\!=s^7 \wedge s'^7 = s^8_0 \wedge s^8_{m_1+m_2}\!=\!s'\\
~~\\
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2}\!\! \vis{\set{\beta^6_i}}
\dotcup\vis{\set{\beta^7}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta^8_i}}
}\\
\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^6_i\land\Pred^7\subst{ \biguplus_{i=0}^{n_2}\Post^6_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred^6_i\subst{\Post^7}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^6_i}}
\\
\displaystyle{\Post= ({x^8_k\gets (e^8_k\subst {\Post^7})\subst{\biguplus_{i=0}^{n_2} \Post^6_i}})^{k\in K}}
$
This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible. 
\end{itemize}
\end{proof}
-----------------------------------------------------

@@

 Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
For any  states
$s\in\mathcal{S}_1$ and
$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
   have:

 \begin{itemize}
 \item  For any open transition $\symb{WOT}$ in $\WT_1$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

@@

\end{corollary}
\begin{proof}
Sketch for discussion.\\
Definition 14 implies definition above

WE SUPPOSE DEF 14, AND 
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

@@

we want
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
with the side conditions ....

1) By lemma \ref{lem-rel-OT-WOT} we have:

\begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}
         \implies

 \Bigg(\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i}} \in \mathcal{T} \quad \wedge
\quad
\openrule
         {
           \set{\beta^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
\quad \wedge\\
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\Bigg) 
 \end{mathpar}

2) on the alpha we apply def 14: From Definition \ref{def-Weak-bisim} we have:

For each open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{j\in J'},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {\alpha} s'}

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

 3) From Definition \ref{def:buildweakOT} we have:

 \begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in \WT
\qquad
\openrule
         {
           \set{\gamma_2},\Pred_2,\Post_2  }
         {s_1 \OTWeakarrow {\alpha} s_2} \in \WT
\qquad
\openrule
         {
           \set{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s_2 \OTWeakarrow {\tau} s'} \in\WT
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_2})\subst{\Post_1}
}
{
\openrule
         {
           \set{\gamma_1}\dotcup \set{\gamma_2}\dotcup\set{\gamma_3},
		\Pred,
				({x_k\gets (e_k\subst {\Post_2})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha} s'} \in\WT
} \WTTrois
\end{mathpar}

 \TODO{Trouver comment decrire la recurrence/fusionner les Pred}

>>>>

By construction, four substitutions $\subst{~}$ only have an effect on the  
variables of the open automaton they belong to, they also produce terms containing only 
variables of the open automaton they belong to. Finally, because of the domain of the 
substitutions  and of the predicates, we have:\\
       	$\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	\Leftrightarrow % we changed =
       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
       	\Pred_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	\Leftrightarrow % we changed = 
       	 \Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $\\

@@

@@

\item By induction hypothesis this means each tau weak open transition can be written as a series of $n_1$ tau transitions such $n_1=n+m+1$, hence by simplification we have (strictly speaking, by induction we might also have the case $\alpha=\tau\land\set \gamma=\emptyset\land \ldots$ but in this case, \WTUn\ allows us to obtain a similar reduction with $n_1=1$): 
\begin{mathpar}
%\inferrule{
\bigg( \openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT \bigg)
\Rightarrow
\bigg( \forall i \in [0\ldots n_1].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}         \bigg)
\end{mathpar}
where \\
$ 
s=s^1_0 \wedge s^1_{n_1}\!=s_1,
\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n_1} \vis{\set{\beta^1_i}}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n_1}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n_1} \Post_i^1\\
$

@@

such that\\
$
s_i^6= \left\{
 \begin{array}{ll}
s_i^1 & \mbox{if }i<n_1\\
s_{i-n_1}^3 & \mbox{if }i\geq n_1\\
\end{array}
\right. \, \wedge \,
s_i^8= \left\{
 \begin{array}{ll}
s_i^2 & \mbox{if }i<m_1\\
s_{i-m_1}^5 & \mbox{if }i\geq m_1\\
\end{array}
\right. \\
s\!=\!s^6_0 \wedge s^6_{n_1+n_2}\!=s^7 \wedge s'^7 = s^8_0 \wedge s^8_{m_1+m_2}\!=\!s'\\
~~\\
\displaystyle{\set{\gamma}=\mybigdotcup_{i=0}^{n_1+n_2}\!\! \vis{\set{\beta^6_i}}
\dotcup\vis{\set{\beta^7}}\dotcup\!\mybigdotcup_{i=0}^{m_1+m_2}\!\!\vis{\set{\beta^8_i}}
}\\
\displaystyle{\Pred=\bigwedge_{i=0}^{n_2}\Pred^6_i\land\Pred^7\subst{ \biguplus_{i=0}^{n_2}\Post^6_i}\land \Big(\bigwedge_{i=0}^{m_2}\Pred^6_i\subst{\Post^7}\Big)\subst{\biguplus_{i=0}^{n_1}\Post^6_i}}
\\
\displaystyle{\Post= ({x^8_k\gets (e^8_k\subst {\Post^7})\subst{\biguplus_{i=0}^{n_2} \Post^6_i}})^{k\in K}}
$\\
This concludes the inductive step, showing  that the decomposition expressed by the $\Leftarrow$ direction of the lemma is always possible. 
\end{itemize}
\end{proof}
-----------------------------------------------------

@@

 Let $A_1 = <J,\mathcal{S}_1, s_0,
    \mathcal{T}_1>$ and $A_2 = <J,\mathcal{S}_2,t_0,  \mathcal{T}_2>$ be open automata.
Let $<J,\mathcal{S}_1, s_0,
    \WT_1>$ and $<J,\mathcal{S}_2,t_0,  \WT_2>$ be the
weak open automata derived from $A_1$ and $A_2$ respectively.
For any  states
$s\in\mathcal{S}_1$ and
$t\in\mathcal{S}_2$ such that $(s,t|\Pred)\in\mathcal{R}$, we 
   have:
\begin{itemize}
 \item  For any open transition $\symb{WOT}$ in $\WT_1$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

@@

\end{corollary}
\TODO{Proof in progress}
\begin{proof} 
($\Rightarrow$) Firstly, we prove that Definition \ref{def-Weak-bisim} implies definition above.

Suppose that for any open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{j\in J'_1},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {\alpha} s'}

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, \{j\in J'|\beta_j\neq\tau\}=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
 $\Pred \land \Pred_{OT}\\
 \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
   \left(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x\land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)$

and  suppose we have:
\begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

\end{mathpar}
By using lemma \ref{lem-rel-OT-WOT} we have:
\begin{mathpar}
    \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}
         \implies
\bigg(\forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i}} \in \mathcal{T}  \wedge

\openrule
         {
           \beta_j^{J^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} \in \mathcal{T}
 \wedge
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}} \in \mathcal{T}
\bigg)
\end{mathpar}
The (\WTDeux)~ and (\WTTrois)~  rules can be applied repeatedly to produce:
\begin{mathpar}
%\inferrule{
 \forall i \in [0\ldots n].\openrule
    {
       \set{\beta^1_i},\Pred^1_i,\Post^1_i   }
         {s^1_i \OTarrow {\tau} s^1_{i+1}} \in \mathcal{T}          \implies
 \openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} \in\! \WT 
\end{mathpar}
where 
\begin{mathpar}
s=s^1_0 \wedge s^1_{n}\!=s_1,
\displaystyle{\set{\gamma_1}=\mybigdotcup_{i=0}^{n} \vis{\set{\beta^1_i}}}, 
\Pred_1\!=\!\bigwedge_{i=0}^{n}\Pred^1_i, \Post_1= \biguplus_{i=0}^{n} \Post_i^1\\
\end{mathpar}
And similarly, a series of $m$ open transitions can be simplified:
\begin{mathpar}
%\inferrule{
\forall i \in [0\ldots m].\openrule
         {
           \set{\beta^3_i},\Pred\,^3_i,({x^3_k\!\gets e^3_k})^{k\in K}    }
         {s^3_i \OTarrow {\tau} s^3_{i+1}}\! \in\! \mathcal{T}       
          \!\implies\!
\openrule
         {
           \set{\gamma_3},\Pred_3, ({x_k\!\gets e_k})^{k\in K}}
         {s_2 \OTWeakarrow {\tau} s'}\! \in\! \WT 
\end{mathpar}
where 
\begin{mathpar}
s_2=s^3_0 \wedge s^3_{m}\!=s',
\displaystyle{\set{\gamma_3}=\mybigdotcup_{i=0}^{m} \vis{\set{\beta^3_i}}}, 
\Pred_3\!=\!\bigwedge_{i=0}^{m}\Pred^3_i 
%\Post_3= \biguplus_{i=0}^{n_1} \Post_i^1\\
\end{mathpar}
Concerning the middle open transition, by Definition \ref{def-Weak-bisim} we know that for each open transition $OT$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_j^{J^2},\Pred\,^2,\Post^2 }
         {s^2 \OTarrow {\alpha} s'^2} 
\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x,J^2=J_{x}, (s'^2,t_x|\Pred_{s'^2,t_x})\in \mathcal{R}$; 
 and  \TODO{$\{j\in J^2|\beta_j\neq\tau\}$ useless} \\
 $\Pred \land \Pred\,^2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}}
   \left( \forall j\in J_x. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s'^2,t_x}\subst{\Post^2}\subst{\Post_{OT_x}}\right)$

On other hand, by applying (\WTTrois)~rule  on each  $\symb{WOT}_x$ we have:

 \begin{mathpar}
  \mprset {vskip=.5ex}
\inferrule {\openrule
         {
           \set{\gamma_1},\Pred_1,\Post_1   }
         {s \OTWeakarrow {\tau} s_1} 
\qquad
\openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\qquad
\openrule
         {
           \set{\gamma_3},\Pred_3,({x_k\gets e_k})^{k\in K}    }
         {s_2 \OTWeakarrow {\tau} s'} 
\\
\Pred=\Pred_1\land\Pred_2\subst{\Post_1}\land (\Pred_3\subst{\Post_{OT_x}})\subst{\Post_1}
}
{
\openrule
         {
           \set{\gamma_1}\dotcup\gamma_{j x}^{j\in J_{x}} \dotcup\set{\gamma_3},
		\Pred,
				({x_k\gets (e_k\subst {\Post_{OT_x}})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha_x} s'} 
} 
 \end{mathpar}
such that
$s_1=t \wedge t_x=s_2$  \TODO{Attention les states; I'm not convinced}\\
Therefore, we can deduce that:

For any open transition $\symb{WOT}$ in $\WT_1$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
 {
\openrule
         {
           \set{\gamma_1}\dotcup\gamma_{j x}^{j\in J_{x}} \dotcup\set{\gamma_3},
		\Pred,
				({x_k\gets (e_k\subst {\Post_{OT_x}})\subst{\Post_1}})^{k\in K} } 
         {s \OTWeakarrow {\alpha_x} s'} 
}     
\end{mathpar}
\TODO{Side Conditions to discuss}\\
 such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
$\Pred \land \Pred_{OT}\\
\displaystyle{\implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x.\gamma_j=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)}$

\noindent ($\Leftarrow$) Now, we prove that the definition above implies Definition \ref{def-Weak-bisim}.

Suppose that for any weak open transition $\symb{WOT}$ in $\WT_1$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

and suppose that we have:
\begin{mathpar}
     \openrule
         {
           \beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {\alpha} s'}

@@

By applying (\WTDeux)~rule we can directly deduce that we have:

\begin{mathpar}
     \openrule
         {
           \vis{\beta_j^{j\in J_1}},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'}

Then by transitivity,   it is straightforward to  deduce that for any open transition $\symb{OT}$ in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
         {s \OTarrow {\alpha} s'}

\end{mathpar}
 there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\alpha_x} t_x}
\end{mathpar}
 such that  $\forall x, J_1=J_{x}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
 and  \\
$\Pred \land \Pred_{OT}\\
\displaystyle{\implies\!\!\! \bigvee_{x\in X}
   \left( \forall j\in J_x.\vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_x}
     \land \alpha\!=\!\alpha_x \land  
     \Pred_{s',t_x}\subst{\Post_{OT}}\subst{\Post_{OT_x}}\right)}$
